Adopting agile software development in the large organizations: A systematic literature review

### 2014-06-04 journal/article.tex
Editing: Success factors

Yet another factor pushing for improvement was the need to accommodate change
during development. Organizations saw agile as an opportunity to improve
responsiveness to change in general [P25, P26, P42].
Some organizations faced difficulties when changes to plans were needed. For
instance, the organizational structure made adapting to changes difficult [52],
and making changes created management overhead [P51]. Other organizations saw an
business advantage in enabling priorities to be changed as required [P8, P39].
Domain knowledge will deepen during projects and environments will inevitably
change, and therefore the requirements should not stay fixed [P4].
Customers and business representatives were in many cases attributed as the
sources of change requests, and the responsiveness to customer requests needed
to be improved [P18, P33, P36, P49].

@@

The typical first task of the change team was to decide on an alternative
delivery method to solve problems in the old model [P21, P30]. During the
transformation the team stimulated agile adoption in the organization [P18, P45,
P49]. Other examples on thechange team's tasks were informing people on the
agile model [P4], educating and coaching [P16, P45, P48, P49], creating an agile
cookbook [P23], and organizing presentations and workshops [P25, P41]. The
change team also assessed the success of transformed teams, and worked for
repeating their success across the organization [P16, P40, P41]. The change team
was empowered to act on removing impediments they discovered [P16, P50].

@@

% Why
Coaching was considered necessary, especially in the beginning of agile projects
[P6, P8, P33, P46, 47]. Brown [P8] stated that without adequate coaching there
would have been severe long term consequences [P8]. The application of coaching
was seen as an important success factor [P18, P29, P33], and the job of the
coach was described to be to ensure that the transformation would be successful
[P16]. One viewpoint was that the coach was an impartial third party who could
be relied on when resolving transformation impediments [P16, P29, P44].

% Having too little coaches [23].
% Coaches were also involved in training [P27].

@@

Development is traditionally preceded by requirements engineering and succeeded
by quality assurance (QA) activities. Agile methods suggest that essential parts
of these activities would be performed within the development team. However,
when developing large systems the effort required for managing requirements and
QA may be too heavy for individual teams to handle. Table
\ref{table:challenges_requirementsandqa} presents challenges in implementing
additional requirements management and quality assurance required in large
development projects.

@@

A phenomena that troubled some organizations was over-enthusiasm towards agile
methods. In several cases there was mentionings about change leaders or teams
becoming agile zealots. For instance, Evans [12] describes how some members of
the agile community were becoming too evangelic, which made people take sides
for or against agile development. In another case team members started out with
an overly eager attitude, but when agile did not deliver improvements the
interest faded and started to go back to the old process [P20]. Attempting to
implement agile too strictly may cause conflicts, and especially in a large
organization the change leaders need to maintain a collaborative attitude
towards various groups in the surrounding organization [P6]. Introducing agile
methods does not guarantee success, and therefore they should not be followed
blindly [P4].

@@

\begin{table}[h]
    \centering
    \begin{tabular}{ >{\raggedright\arraybackslash}p{0.51\textwidth}
                     >{\raggedright\arraybackslash}p{0.41\textwidth} }
        \toprule
        Success factors  &  Described in \\
        \midrule
        Training is necessary to achieve change  &
                P3, P6, P11, P14, P16, P30, P37, P46 \\
        Coaching is essential in transformation  &
                P3, P6, P8, P9 P16, P17, P18, P29, P30, P33, P42, P44, P47, P48  \\
        \bottomrule
    \end{tabular}
    \caption{XXXXXXXXXXXXXX}
    \label{table:success_NN}
\end{table}

Training was seen as a strong factor helping the organization to transform.
Several studies stated that training improved the chance of succeeding in the
transformation [P3, 16, P30]. It was even highlighted that the change would have
failed without transformation [P14]. As Benefield [P6] claimed: ``we saw again
and again how training could make the difference between success and failure for
a team''. Training also helped people to become more positively inclined towards
the new model [P16, P37], and at best training made people enthusiastic to change
[P3, P46]. A few cases reported that there was some disinclination to change,
and training would have helped to overcome [P11, P14].

@@

\subsubsection{Choosing the agile model}

The choice of agile practices did affect the success of the transformation, and
also how the practices were chosen affected.

@@

Customizing the agile model and practices was reported as an necessary step in
the agile implementation. As each organization will have its own challenges in
adopting agile, it should be carefully considered which organization specific
areas to focus on when choosing the agile practices to implement  [P8, P43].
Lewis and Nehrer [P29] recommended to choose the agile model according to the
current corporate model in order to avoid interference.

Cases reported that customization was part of a successful agile implementation.
For instance, teams were let to customize their practices individually, to fit
the needs of each team [P41].
Spayd [P49] writes that teams who modified agile practices to suite the large and
distributed environment ended up doing better than teams that did not.
% Some intermediate point?
To allow teams to become innovative and perform well the agile model should be
customized in a pragmatical way instead of following a strict textbook
interpretation [P10]

The customization of the agile model was also seen as an evolutionary process.
Cowan [11] suggested that in a big-bang transformation it might be necessary to
selectively compromise some parts of the agile implementation so that the core
practices can be set in place.
The agile transformation is a constantly ongoing process, and it is recommended
to regularly challenge teams to refine the agile implementation to reflect the
current needs of the organization [P41, P43].

% Customize the agile model?
% ??
% [P16]
% This cross-functional team redesigned and rebuilt the development process from
% the ground up using key values from the company’s founding: KISS (Keep it Simple
% Stupid), iterate quickly, and listen to our customers. These values are a
% natural match for agile methodologies.
% 
% ??? There are changes done to the agile proces, but doing it is not that much emphasized
% [P51]
% One after the other, all products where then switched to the new Scrum process.
% Along the way, minor adjustments were often made. The teams were constantly
% searching for the right balance between sprint duration, size estimation,
% requirement size, and time spent on backlog administration. Changes to the
% process were initially often managed by the the CTO. However, they were
% increasingly delegated to the appropriate ScrumMasters.
% Comment: This is not directly seen as a success factor.

% ??
In order to draw the most out of agile teams should innovate and find on
practices that really work for their case [P40, P41]

\subsubsection{Considering other parts than development}

@@

A particular role that seemed to make much difference in the agile introduction
was the Product Owner. Many cases reported on problems if the Product Owner did
not perform adequately, and it was seen as critical to have a dedicated person
in that role [P12, 14, P30, P39].
Success or problems emerged respectively depending on how well the Product
Owners were performing. In one case a well implemented Product Owner role was
understood to be a key success factor when using agile methods [16, P33].
It was reported that when the Product Owner role was implemented correctly the
team performed better and the work products were correct [P24]. Projects started
off better when the Product Owners were engaged early on, and some Product
Owners even became agile enthusiasts when they learned how business and
technology can collaborate in the agile model [P46].

@@

\subsubsection{Create a positive start by piloting}

The agile model was usually tried out in the organization before rolling it out
on a general level. Having a pilot project was reported as a significant success
factor in several cases [P3, P9, P38].
The pilot project gave proof that the agile model would be suitable for the
organization and the general acceptance of agile was increased [P3, 17].
The pilot also cleared disbeliefs of the suitability of agile for large
organizations, and created acceptance for both development and management [P9,
P31, P36].

@@

@@

The most prominent and clear success factor was having support from management.
Numerous cases made it clear that management support is an absolute necessity
[P8, P18, P27, P31, P33, P36, P43, P47, P49].
This was reflected in statements such as ``Adopting agile, or implementing any
significant change, requires an executive’s sincere support.'' [P44],
``Executive commitment was crucial to implementing massive change.'' [P16], and
``Having upper management engaged, supportive and visible is critical for
wholesale organization involvement with Scrum.'' [P11].

>>>>

Yet another factor pushing for improvement was the need to accommodate change
during development. Organizations saw agile as an opportunity to improve
responsiveness to change in general [P25, P26, P42].
Some organizations faced difficulties when changes to plans were needed. For
instance, the organizational structure made adapting to changes difficult [P52],
and making changes created management overhead [P51]. Other organizations saw an
business advantage in enabling priorities to be changed as required [P8, P39].
Domain knowledge will deepen during projects and environments will inevitably
change, and therefore the requirements should not stay fixed [P4].
Customers and business representatives were in many cases attributed as the
sources of change requests, and the responsiveness to customer requests needed
to be improved [P18, P33, P36, P49].

@@

The typical first task of the change team was to decide on an alternative
delivery method to solve problems in the old model [P21, P30]. During the
transformation the team stimulated agile adoption in the organization [P18, P45,
P49]. Other examples on the change team's tasks were informing people on the
agile model [P4], educating and coaching [P16, P45, P48, P49], creating an agile
cookbook [P23], and organizing presentations and workshops [P25, P41]. The
change team also assessed the success of transformed teams, and worked for
repeating their success across the organization [P16, P40, P41]. The change team
was empowered to act on removing impediments they discovered [P16, P50].

@@

% Why
Coaching was considered necessary, especially in the beginning of agile projects
[P6, P8, P33, P46, P47]. Brown [P8] stated that without adequate coaching there
would have been severe long term consequences [P8]. The application of coaching
was seen as an important success factor [P18, P29, P33], and the job of the
coach was described to be to ensure that the transformation would be successful
[P16]. One viewpoint was that the coach was an impartial third party who could
be relied on when resolving transformation impediments [P16, P29, P44].

% Having too little coaches [P23].
% Coaches were also involved in training [P27].

@@

Development is traditionally preceded by requirements engineering and succeeded
by quality assurance (QA) activities. Agile methods suggest that essential parts
of these activities would be performed within the development team. However, for
large systems the effort required for managing requirements and QA may be too
heavy for individual teams to handle. For instance, a single development team
can manage and elaborate items in its own backlog, but a large feature may
require work across many teams. The feature needs to be divided to team specific
items on a higher level, and the process must be managed somehow.
Table \ref{table:challenges_requirementsandqa} presents challenges in
implementing additional requirements management and quality assurance required
in large development projects.

@@

A phenomena that troubled some organizations was over-enthusiasm towards agile
methods. In several cases there was mentionings about change leaders or teams
becoming agile zealots. For instance, Evans [P12] describes how some members of
the agile community were becoming too evangelic, which made people take sides
for or against agile development. In another case team members started out with
an overly eager attitude, but when agile did not deliver improvements the
interest faded and started to go back to the old process [P20]. Attempting to
implement agile too strictly may cause conflicts, and especially in a large
organization the change leaders need to maintain a collaborative attitude
towards various groups in the surrounding organization [P6]. Introducing agile
methods does not guarantee success, and therefore they should not be followed
blindly [P4].

@@

Agile methods come as new ways of working to many in the organization. In order
to get a good start in the transformation the ideas of the new methods need to
be explained thoroughly. Training sessions are good starting points, but teams
should be accompanied by coaching for a longer time to ensure that the new
practices are learned and applied correctly in practice. Table
\ref{table:success_training} lists references that highlight training and
coaching as success factors.

\begin{table}
    \centering
    \begin{tabular}{ >{\raggedright\arraybackslash}p{0.51\textwidth}
                     >{\raggedright\arraybackslash}p{0.41\textwidth} }
        \toprule
        Success factors  &  Described in \\
        \midrule
        Providing training on agile methods  &
                P3, P6, P11, P14, P16, P30, P37, P46 \\
        Coaching teams as they learn by doing  &
                P3, P6, P8, P9 P16, P17, P18, P29,
                P30, P33, P42, P44, P47, P48  \\
        \bottomrule
    \end{tabular}
    \caption{Training and coaching presented as success factors}
    \label{table:success_training}
\end{table}

Training was seen as a strong factor helping the organization to transform.
Several studies stated that training improved the chance of succeeding in the
transformation [P3, P16, P30]. It was even highlighted that the change would have
failed without transformation [P14]. As Benefield [P6] claimed: ``we saw again
and again how training could make the difference between success and failure for
a team''. Training also helped people to become more positively inclined towards
the new model [P16, P37], and at best training made people enthusiastic to change
[P3, P46]. A few cases reported that there was some disinclination to change,
and training would have helped to overcome [P11, P14].

@@

\subsubsection{Use of piloting}

The agile model was usually tried out in the organization before rolling it out
on a general level. Beyond being a common practice, the use of pilot programs
was also attributed as a success factor. Table \ref{table:success_pilots} lists
sources discussing piloting as a success factor.

\begin{table}
    \centering
    \begin{tabular}{ >{\raggedright\arraybackslash}p{0.51\textwidth}
                     >{\raggedright\arraybackslash}p{0.41\textwidth} }
        \toprule
        Success factors  &  Described in \\
        \midrule
        Have a pilot project at start  &
                P3, P9, P14, P17, P31, P36, P38, P39, P47  \\
        Gather insights from pilot projects  &
                P8, P22, P27, P40, P45  \\
        \bottomrule
    \end{tabular}
    \caption{Piloting the agile model as a success factor}
    \label{table:success_pilots}
\end{table}

Having a pilot project was reported as a significant success factor in several
cases [P3, P9, P38].
The pilot project gave proof that the agile model would be suitable for the
organization and the general acceptance of agile was increased [P3, P17].
The pilot also cleared disbeliefs of the suitability of agile for large
organizations, and created acceptance for both development and management [P9,
P31, P36].

\subsubsection{Choosing the agile model to fit the organization}

The choice of agile practices did affect the success of the transformation. It
was common that cases described that it was beneficial to customize agile
practices to fit the organization specific environment. As agile models do not
prescribe practices strictly there was opportunities to make choices in the
implementation. A few recommendations were given for choosing the agile model,
such as using the same practices for all teams, mapping to the old model, and
keeping practices simple. Table \ref{table:success_choosemodel} lists viewpoints
relating to the choice of the agile model which were reported to provide
benefits.

\begin{table}
    \centering
    \begin{tabular}{ >{\raggedright\arraybackslash}p{0.51\textwidth}
                     >{\raggedright\arraybackslash}p{0.41\textwidth} }
        \toprule
        Success factors  &  Described in \\
        \midrule
        Customizing the agile model  &
                P8, P10, P11, P29, P31, P40, P41, P43, P45, P49, P51  \\
        Conformity to a single agile model  &
                P8, P11, P12, P16, P32, P43  \\
        Mapping to the old model eases adaptation  &
                P14, P29, P44, P46, P48  \\
        Keeping the new model simple  &
                P5, P10, P16, P40  \\
        \bottomrule
    \end{tabular}
    \caption{Recommendations for choosing the agile model}
    \label{table:success_choosemodel}
\end{table}

Customizing the agile model and practices was often seen as an necessary step in
the agile implementation. As each organization will have its own challenges in
adopting agile, it should be carefully considered which organization specific
areas to focus on when choosing the agile practices to implement [P8, P43].
Lewis and Nehrer [P29] recommended to choose the agile model according to the
current corporate model in order to avoid interference.

Cases reported that customization was part of a successful agile implementation.
For instance, teams were let to customize their practices individually, to fit
the needs of each team [P41].
Spayd [P49] writes that teams who modified agile practices to suite the large and
distributed environment ended up doing better than teams that did not.
% Some intermediate point?
To allow teams to become innovative and perform well the agile model should be
customized in a pragmatical way instead of following a strict textbook
interpretation [P10]
In order to draw the most out of agile teams should innovate and find on
practices that really work for their case [P40, P41]

The customization of the agile model was also seen as an evolutionary process.
Cowan [P11] suggested that in a big-bang transformation it might be necessary to
selectively compromise some parts of the agile implementation so that the core
practices can be set in place.
The agile transformation is a constantly ongoing process, and it is recommended
to regularly challenge teams to refine the agile implementation to reflect the
current needs of the organization [P41, P43].

@@

\subsubsection{Considering the Product Owner role and requirements management}

A particularly difficult part to implement efficiently was requirements
management work. The key role in handling requirements is the Product Owner.
Many cases described that careful attention to the requirements management roles
was necessary for a successful transformation.
Table \ref{table:success_requirements} lists references that discuss careful
implementation of the product owner role and requirements management as success
factors.

\begin{table}
    \centering
    \begin{tabular}{ >{\raggedright\arraybackslash}p{0.51\textwidth}
                     >{\raggedright\arraybackslash}p{0.41\textwidth} }
        \toprule
        Success factors  &  Described in \\
        \midrule
        Pay attention to the Product Owner role  &
                P12, P14, P16, P24, P30, P33, P39, P46  \\
        Pay attention to requirements management  &
                P5, P11, P17, P33, P48  \\
        \bottomrule
    \end{tabular}
    \caption{Careful implementation of requirements management seen as a
             success factor}
    \label{table:success_requirements}
\end{table}

A particular role that seemed to make much difference in the agile introduction
was the Product Owner. Many cases reported on problems if the Product Owner did
not perform adequately, and it was seen as critical to have a dedicated person
in that role [P12, P14, P30, P39].
Success or problems emerged respectively depending on how well the Product
Owners were performing. In one case a well implemented Product Owner role was
understood to be a key success factor when using agile methods [P16, P33].
It was reported that when the Product Owner role was implemented correctly the
team performed better and the work products were correct [P24]. Projects started
off better when the Product Owners were engaged early on [P46]. Some Product
Owners were even described to become agile enthusiasts when they learned how
business and technology can collaborate in the agile model [P46].

@@

The most prominent and clear success factor was having support from management.
When the leadership of the organization is committed and supportive change is
much more likely to happen. Table \ref{table:success_management} lists
success factors related to management support.

\begin{table}
    \centering
    \begin{tabular}{ >{\raggedright\arraybackslash}p{0.51\textwidth}
                     >{\raggedright\arraybackslash}p{0.41\textwidth} }
        \toprule
        Success factors  &  Described in \\
        \midrule
        Have management support  &
                P8, P11, P16, P18, P27, P31, P33, P36,
                P43, P44, P46, P47, P49  \\
        Visible management support encourages employees  &
                P9, P11, P24, P40  \\
        Educate management on agile methods  &
                P6, P8, P9, P11, P16, P29, P35, P46, P47  \\
        \bottomrule
    \end{tabular}
    \caption{Success factors relating to management support for agile}
    \label{table:success_management}
\end{table}

Numerous cases made it clear that management support is an absolute necessity
[P8, P18, P27, P31, P33, P36, P43, P47, P49].
This was reflected in statements such as ``Adopting agile, or implementing any
significant change, requires an executive’s sincere support.'' [P44],
``Executive commitment was crucial to implementing massive change.'' [P16], and
``Having upper management engaged, supportive and visible is critical for
wholesale organization involvement with Scrum.'' [P11].

@@

@@

%         Emphasizing principles over mechanics  &
%                 P1, P16, P32, P42, P46, P48  \\

@@
